Dependent Object Types

### 2012-08-09 article.tex
sprinkled todos in logical relation section

@@

@@

@@

@@

@@

>>>>

\todo{quick intro that explains the general approach of step-indexed
  logical relations and the strategy here of setting up $\ds$ in terms
  of $\mathcal{E}$ -- give an overview of what's coming}

@@

\todo{mention possible pitfall: we are not checking type labels of a
  semantic value, yet because we're substituing the value for the
  ``self'' in the expansion, the value and its type labels show up and
  are constrained by T.}

@@

\todo{irred is never formally defined (easy one!)}
\todo{explain the strange ! notation, or make it more intuitive}
\todo{briefly introduce the extensions to env and store before they are used}

@@

\todo{expand on why this non-trivial subcase is all that is needed for each case.}

@@

\todo{possible pitfall with narrowing needs more cautiousness}

@@

\todo{explain that this is the reason why extending the store is so
  flexible}
